### 2016-04-04 text/ms.Rmd
Wrap text to work in vim by voice

\bigskip
\noindent
\textbf{Abstract:} Fishery managers must often reconcile conflicting estimates of population status and trend. One solution is to average predictions using an ensemble method, but this approach ignores covariance between models and may not optimally reduce bias and improve accuracy. Superensemble models, commonly used in climate and weather forecasting, may provide a superior solution. Superensembles use predictions from multiple models as covariates in an additional model. By training this superensemble model using known data, we can then use it to predict unknown situations. We evaluated the potential for ensemble and superensemble models ('ensemble methods') to improve estimates of population status and trend for fisheries. We fit four widely applicable data-limited models that estimate stock biomass relative to the equilibrium biomass at maximum sustainable yield ($B/B_\mathrm{MSY}$). We combined the models' estimates to build four ensemble methods: an ensemble average and three superensembles (a linear model, a random forest, and a boosted regression tree). We used the ensemble methods to predict both (i) fishery status and (ii) recent trends of $B/B_\mathrm{MSY}$. We trained our models on a simulated dataset of 5760 stocks and tested them with cross-validation and against a global database of `r ram_stocks_n` real stock assessments. We found that ensemble methods substantially improved estimates of population status and trend. Random forest and boosted regression trees performed the best for estimating population status: accuracy improved `r mean_sim$mach_vs_ind_mare_fold`%, rank-order correlation between predicted and true status improved from `r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range` across models?, and bias (median proportional error) declined from `r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range`. We found similar improvements when predicting the trend of status and when applying the simulation-trained superensembles to catch data for global fish stocks. Ensemble methods can improve estimates of status and trends; however, they must be tested, formed from a diverse set of accurate models, and built on a dataset representative of the populations to which they are applied. *TODO: Still need to cut ~30 words*

@@

<!--TODO Kristin and Mark: It might be a good idea to add a figure that illustrates the spectrum of ensemble/superensembles that are applied here and what is included (e.g., non-linear relationships, etc.). This will help the reader understand the progression in complexity of the ensemble approaches I think. 
Jess: probably add this below the section explaining superensembles-->
<!-- TODO deal with removed spectral -->
<!-- 
Superensemble models allow us to incorporate additional covariates and potentially leverage interactions between these covariates and individual model predictions. Additional covariates could be, for example, life-history characteristics, information on exploitation patterns, or statistical properties of the data. For simplicity, and since many possible covariates, such as fishing effort dynamics, would not be known for many real-world data-limited scenarios, we added only one set of additional covariates: spectral properties of the catch time series. Spectral analysis decomposes a time series into the frequency domain and provides a means of describing the cyclical shape of the catch series that is independent of time series length (except in affecting precision) and absolute magnitude of catch. We fit spectral models to the scaled catch time series (catch divided by maximum catch) with the `spec.ar` function in R and recorded representative short- and long-term spectral densities at frequencies of 0.20 and 0.05, which correspond to 5- and 20-year cycles.
-->

@@

The superensemble models were able to improve the predictive performance by harnessing the best properties of individual models, the covariance between individual models, and interactions with other covariates. For example, SSCOM had strong predictive ability when it predicted low $B/B_\mathrm{MSY}$ (Fig. \ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were approximately linearly related to $B/B_\mathrm{MSY}$ within the low and high clusters of predictions (Fig. \ref{partial-sim}). Superensembles also exploited the covariance between individual model predictions. For instance, both the linear model and GBM ensemble suggest that if mPRM and SSCOM predict high status, the true status also tends to be high (Figs \ref{lm-coefs}, \ref{partial-2d-sim}l). The addition of spectral density covariates helped the superensemble models correctly predict higher status values (Fig. \ref{hexagon}g, h) due to the interactions between the spectral density predictors and the individual model predictors (Fig. \ref{partial-2d-sim}). Although the additional covariates improved ensemble fit, performance of the ensembles was only marginally degraded by removing these covariates (Fig. \ref{hexagon} vs. Fig. \ref{hexagon-sim-basic}).
<!--TODO trash this?-->

>>>>

\noindent \textbf{Abstract:} Fishery managers must often reconcile conflicting
estimates of population status and trend. One solution is to average
predictions using an ensemble method, but this approach ignores covariance
between models and may not optimally reduce bias and improve accuracy.
Superensemble models, commonly used in climate and weather forecasting, may
provide a superior solution. Superensembles use predictions from multiple
models as covariates in an additional model. By training this superensemble
model using known data, we can then use it to predict unknown situations. We
evaluated the potential for ensemble and superensemble models ('ensemble
methods') to improve estimates of population status and trend for fisheries. We
fit four widely applicable data-limited models that estimate stock biomass
relative to the equilibrium biomass at maximum sustainable yield
($B/B_\mathrm{MSY}$). We combined the models' estimates to build four ensemble
methods: an ensemble average and three superensembles (a linear model, a random
forest, and a boosted regression tree). We used the ensemble methods to predict
both (i) fishery status and (ii) recent trends of $B/B_\mathrm{MSY}$. We
trained our models on a simulated dataset of 5760 stocks and tested them with
cross-validation and against a global database of `r ram_stocks_n` real stock
assessments. We found that ensemble methods substantially improved estimates of
population status and trend. Random forest and boosted regression trees
performed the best for estimating population status: accuracy improved `r
mean_sim$mach_vs_ind_mare_fold`%, rank-order correlation between predicted and
true status improved from `r mean_sim$ind_corr_range` to `r
mean_sim$mach_corr_range` across models?, and bias (median proportional error)
declined from `r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range`. We
found similar improvements when predicting the trend of status and when
applying the simulation-trained superensembles to catch data for global fish
stocks. Ensemble methods can improve estimates of status and trends; however,
they must be tested, formed from a diverse set of accurate models, and built on
a dataset representative of the populations to which they are applied. *TODO:
Still need to cut ~30 words*

@@

<!--TODO Kristin and Mark: It might be a good idea to add a figure that
illustrates the spectrum of ensemble/superensembles that are applied here and
what is included (e.g., non-linear relationships, etc.). This will help the
reader understand the progression in complexity of the ensemble approaches
I think. Jess: probably add this below the section explaining superensembles-->
<!-- TODO deal with removed spectral -->

<!-- Superensemble models allow us to incorporate additional covariates and
potentially leverage interactions between these covariates and individual model
predictions. Additional covariates could be, for example, life-history
characteristics, information on exploitation patterns, or statistical properties
of the data. For simplicity, and since many possible covariates, such as fishing
effort dynamics, would not be known for many real-world data-limited scenarios,
we added only one set of additional covariates: spectral properties of the catch
time series. Spectral analysis decomposes a time series into the frequency
domain and provides a means of describing the cyclical shape of the catch series
that is independent of time series length (except in affecting precision) and
absolute magnitude of catch. We fit spectral models to the scaled catch time
series (catch divided by maximum catch) with the `spec.ar` function in R and
recorded representative short- and long-term spectral densities at frequencies
of 0.20 and 0.05, which correspond to 5- and 20-year cycles. -->

@@

The superensemble models were able to improve the predictive performance by
harnessing the best properties of individual models, the covariance between
individual models, and interactions with other covariates. For example, SSCOM
had strong predictive ability when it predicted low $B/B_\mathrm{MSY}$ (Fig.
\ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were approximately
linearly related to $B/B_\mathrm{MSY}$ within the low and high clusters of
predictions (Fig. \ref{partial-sim}). Superensembles also exploited the
covariance between individual model predictions. For instance, both the linear
model and GBM ensemble suggest that if mPRM and SSCOM predict high status, the
true status also tends to be high (Figs \ref{lm-coefs}, \ref{partial-2d-sim}l).
The addition of spectral density covariates helped the superensemble models
correctly predict higher status values (Fig. \ref{hexagon}g, h) due to the
interactions between the spectral density predictors and the individual model
predictors (Fig. \ref{partial-2d-sim}). Although the additional covariates
improved ensemble fit, performance of the ensembles was only marginally degraded
by removing these covariates (Fig. \ref{hexagon} vs. Fig.
\ref{hexagon-sim-basic}).

<!--TODO trash this?-->
